Generative Adversarial Networks

### 2017-12-03 cs6735/project/report.tex
finished editing

\begin{abstract}
    Within the past decade, deep generative networks have often fallen short, especially when compared to deep discriminative models which are now being applied to a multitude of real world applications. However, since their inception in 2014, generative adversarial networks (GANs) have proved themselves as promising a research avenues for deep generative models. These networks now offer encouraging results for both unsupervised learning and generative models. The goal of this research paper is to present an overview of generative adversarial networks. Specifically, we will examine the motivation and challenges associated with GANs, their training process, architecture variations and some applications that are currently being explored.
\end{abstract}

@@

\subsubsection{Image-to-Image Translation}
Image-to-image translation has shown astounding progress recently and offers many yet undiscovered applications \citep{2017arXiv170100160G}. This includes to process of translating from a source domain $X$ to the target domain $Y$. An example of this process can be visualized in figure \ref{fig:img2img}. Conditional networks are well suited for this task and are used within several different GAN architectures which attempt to solve this problem \citep{2016arXiv161107004I, 2017arXiv171111585W, 2017arXiv170310593Z}. Recent work by Zhu \textit{et al.} demonstrate the feasibility of unpaired image-to-image translation by introducing a cycle consistency loss to enforce $F(G(X)) \approx X$ where $G$ is the mapper and $F$ is the inverse mapper \citep{2017arXiv170310593Z}. Furthermore, research recently released in November 2017 by Wang \textit{et al.} further improve the quality of synthesized images \citep{2017arXiv171111585W}. Generated images from semantic maps are now almost indistinguishable from real images.

@@

\subsection{Semi-Supervised Learning} \label{sec:semisupervised}
There exist several methods for training a classifier using a GAN. These methods all take advantage of the unsupervised aspect of GANs to implement semi-supervised learning and offer a quantitative method to rank different GAN models. One general transfer learning technique involves the use of discriminator within classification tasks as a feature extractor. A new machine learning model, such as a SVM, is subsequently able to be trained on the extracted features of some layer $l$ of the discriminator. Another transfer learning approach makes use of the inference GANs mentioned in section \ref{sec:inferencegan}. Another machine learning model is trained on the last three hidden layers of the of the encoder. These techniques have both received state-of-the-art classification results \citep{2017arXiv171007035C}.

Another general approach to semi-supervised learning transforms the discriminator into a classifier of $k + 1$ classes where $k$ is the amount of real object classes. In this format, the $k + 1$ class is associated with a fake image. When a real image is given to the discriminator, it attempts to classify the sample as one of the k classes; however, when a generated or unlabeled image is given, the probabilities of the k classes are summed together to represent the probability of the image being real. Typical supervised models need more than $50,000$ labels whereas state of the art performance can be achieved on labeled datasets ranging from $20$ to $8,000$ in size \citep{2017arXiv170100160G}.

\subsection{Reinforcement Learning}
Modeling environments offers another promising application for GANs. This capability could potentially be used for reinforcement learning and motion planning. One possible method includes the use of generative models to predict possible futures \citep{2017arXiv170100160G}. The GAN would generate conditional distribution over future states given the current state and an hypothetical action. The agent would make multiple queries to the generator and then choose the action associated with the best possible future. This technique has already been applied by Finn and Levine in 2016 \citep{2016arXiv161000696F}.

Generative models may also be used to maintain a record of past actions and visited locations to aid in future decisions. The connection between GANs and inverse reinforcement learning has also been investigated by Finn \textit{et al.} in 2016 \citep{2016arXiv161103852F}.

\section{Conclusion}
Generative models are currently being applied to many problems \citep{genmodelingopenai}; however, they offer many more possibilities due to their ability to understand the data they are given.

>>>>

\begin{abstract}
    Within the past decade, deep generative networks have often fallen short, especially when compared to deep discriminative models. However, since their inception in 2014, generative adversarial networks (GANs) have proved themselves as promising a research avenues for deep generative models. These networks now offer encouraging results for both unsupervised learning and generative models. The goal of this research paper is to present an overview of generative adversarial networks. Specifically, we will examine the motivation and challenges associated with GANs, their training process, architecture variations and some applications that are currently being explored.
\end{abstract}

@@

\subsubsection{Image-to-Image Translation}
Image-to-image translation has made astounding progress and offers many yet undiscovered applications \citep{2017arXiv170100160G}. This process includes the translation of images from a source domain $X$ to the target domain $Y$. The translated images are then compared against images from the target domain and the generator parameters are updated as to reduce the distance between the translated and real images. An example of this operation can be visualized in figure \ref{fig:img2img}. Conditional networks are well suited for this task and there exists several different GAN architectures which take advantage of their characteristics to preform these translations \citep{2016arXiv161107004I, 2017arXiv171111585W, 2017arXiv170310593Z}. Recent work by Zhu \textit{et al.} demonstrate the feasibility of unpaired image-to-image translation by introducing a cycle consistency loss to enforce $F(G(X)) \approx X$ where $G$ is the mapper and $F$ is the inverse mapper \citep{2017arXiv170310593Z}. Furthermore, research released in November 2017 by Wang \textit{et al.} further improve the general quality of synthesized images \citep{2017arXiv171111585W}. Their semantic map translations are now almost indistinguishable from real images.

@@

\subsection{Semi-Supervised Learning} \label{sec:semisupervised}
There exist several techniques for training a classifier using a GAN. These methods all take advantage of the unsupervised aspect of GANs to implement semi-supervised learning. The ability to use GAN for unsupervised learning also offers a quantitative method to rank different GAN models.

One method involves the use of transfer learning. After the GAN training process has completed, the discriminator may be used within classification tasks as a feature extractor. A new machine learning model, such as a support vector machine (SVM), is trained on the extracted features of some layer $l$ of the discriminator. Another transfer learning approach makes use of the inference GANs mentioned in section \ref{sec:inferencegan}. Similar to the previous technique, a new machine learning model is trained on the last three hidden layers of the of the encoder. These methods have both received state-of-the-art classification results \citep{2017arXiv171007035C}.

Another general approach to semi-supervised learning involves the transformation of the discriminator into a classifier. Given that there are $k$ different labels, the new classifier will have $k + 1$ classes where the $k + 1$ class is associated with a fake image. When a real image is given to the discriminator, it attempts to classify the sample as one of the $k$ classes; however, when a generated or unlabeled image is given, the probabilities of the k classes are summed together to represent the probability of the image being real. In this situation, the classifier reverts back to its discriminative behavior. Typical supervised models need more than $50,000$ samples whereas state of the art performance can be achieved on labeled datasets ranging from $20$ to $8,000$ samples using this technique \citep{2017arXiv170100160G}.

\subsection{Reinforcement Learning}
Modeling environments offers another promising application of GANs. This capability could potentially be used for reinforcement learning and motion planning. One possible method includes the use of generative models to predict possible futures \citep{2017arXiv170100160G}. The GAN would learn a conditional distribution over future states given the current state and a hypothetical action. An agent could make multiple queries to the generator and subsequently choose the action associated with the best possible future. This technique has already been applied by Finn and Levine in 2016 \citep{2016arXiv161000696F}. Generative models may also be used to maintain a record of past actions and visited locations to aid in future decisions \citep{2017arXiv170100160G}.

\section{Conclusion}
GANs are generative models which allow us to parametrize complicated probability distribution functions. They can be used to generate, modify and manipulate images. Furthermore, they allow for the use novel techniques within the context of reinforcement learning and unsupervised learning. Today, they are already being applied to many problems \citep{genmodelingopenai}; however, the majority of their applications have yet to be discovered. As long as the research effort continues, GANs promise exciting new avenues within the field of machine learning.
